Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Fixed the machine specs

All benchmarks are calculated as an average of 5 runs, done in
parallel, on an 11-core, 64-bit Intel Xeon machine running at 2.40GHz
with 11Gb of memory.

>>>>

All benchmarks are calculated as an average of 5 runs, done in
parallel, on an 12-core, 64-bit Intel Xeon machine running at 2.40GHz
with 12Gb of memory.
